Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-26 inst/surfing_jsa.tex
fixes #177

\begin{figure}[h]
  \includegraphics[width=4in]{directplotofstrengths_postinkscape.pdf}  % to create this file, open directplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directplotofstrengths.pdf, with slight optical glitches removed.  File directplotofstrengths.pdf is produced by surfing.Rmd.
\caption{Scatterplot of points scored  \label{compare_likelihood_points}
against maximum likelihood estimates}
\end{figure}

>>>>

\begin{figure}[h]
  \includegraphics[width=4in]{directplotofstrengths_postinkscape.pdf}  % to create this file, open directplotofstrengths_postinkscape.svg in inkscape and export to PDF.  File directplotofstrengths_postinkscape.svg is under version control in the hyper2 github repo.  It is a slight modification of directplotofstrengths.pdf, with slight optical glitches removed.  File directplotofstrengths.pdf is produced by surfing.Rmd.
\caption{Scatterplot of points scored (horizontal
  axis) \label{compare_likelihood_points} against maximum likelihood
  estimates (vertical axis).  One would expect a positive correlation
  as high Bradley-Terry strength would lead to a high probability of
  earning more points; with these axes the correlation is moderate at
  about $R^2=0.71$.  Florence, at $(37700,0.175)$, is something of an
  anomaly. He did not compete at five venues due to injury, this
  affecting his points total but not his likelihood-based
  ranking.}
\end{figure}
